Full-day, in home validation of infant body position measurements from inertial sensors

### 2023-02-12 manuscript.Rmd
group split comparison

```{r setup, include = FALSE}
library("papaja")
library(knitr)
library(patchwork)
library(tidyverse)
```

@@

# Current

@@

# Goal 1: Optimize and validate body position classification model

# Goal 2: Assess classification accuracy across a long delay

# Goal 3: Examine wear time and compliance in full-day data collection

# Goal 4: Compare classification estimates to prior literature

>>>>

```{r setup, include = FALSE}
library(papaja)
library(knitr)
library(patchwork)
library(tidyverse)
library(rstatix)
```

@@

# Current Study

@@

# Results

## Goal 1: Optimize and validate body position classification model
<!--resampled-metrics, splithalf-metrics, predictions CSVs generated from tune_ml/classification_tidymodels.R -->
```{r}
metrics_rs <- read_csv("data/resampled-metrics.csv") 
metrics_sp <- read_csv("data/splithalf-metrics.csv")

```

## Goal 2: Assess classification accuracy over long recordings
<!-- compiled_agreement.csv, generated from analysis-pt2/compile_agreement.R -->

## Goal 3: Compare classification estimates to prior literature
<!-- imu-compiled.csv, generated from analysis-lena-imu/compile_lena_imu.R -->

## Goal 4: Examine wear time and compliance in full-day data collection
<!-- imu-compiled.csv, generated from analysis-lena-imu/compile_lena_imu.R -->
